Using reference models in feature selection problems \vspace{.1in}

### 2019-08-30 paper/ref_approach.tex
less lines in table
modified abstract

\begin{document}
\maketitle
\begin{abstract}
  Feature selection, or more generally, model reduction is an important aspect of statistical workflow aiming to provide insights from data. In this paper we discuss and demonstrate the benefits of using a reference model in model selection in general. A reference model acts as a noise-filter on the target variable by modeling its data generation mechanism. Using the reference model predictions in the model selection reduces tha variability and improves stability leading to improved model selection performance. The simplest reference model approach can be used in combination of common feature selection methods . In several numerical experiments, we show how this translates into better and more stable feature selection independently of the specific selection procedure. 
% These benefits are also illustrated on a real-world example of predicting the amount of body fat for which we compare a reference model based selection method to a purely data driven approach.
\end{abstract}

@@

\begin{table}[tp]
\scriptsize
\centering
\begin{tabular}{l|l|l|l}
  \hline
 Method & Alias & Type & Quantities of interest \\ 
  \hline
 Regularised Horseshoe & RHS & Shrinkage prior & SSE, SESE, $\kappa$ \\
 Dirichlet-Laplace & DL & Shrinkage prior & SSE, SESE, $\kappa$ \\
 Local false discovery rate & loc.fdr & Complete selection & fdr, sensitivity, stability \\
 Median estimator & EB.med & Complete selection & fdr, sensitivity, stability \\
 Credible intervals & ci.90 & Complete selection & fdr, sensitivity, stability \\
 \hline
\end{tabular}
\caption{Summary of the shrinkage and selection methods used in the numerical experiments.}
\label{tab:comparison}
\end{table}

>>>>

\begin{document}
\maketitle
\begin{abstract}
  Feature selection, or more generally, model reduction is an important aspect of statistical workflow aiming to provide insights from data. In this paper we discuss and demonstrate the benefits of using a reference model in model selection in general. A reference model acts as a noise-filter on the target variable by modeling its data generation mechanism. Using the reference model predictions in the model selection reduces the variability and improves stability leading to improved model selection performance. Assuming that a Bayesian reference model describes well the future data distribution, it can be shown that decision theoretically justified approach is to project the reference model to a reduced model leading to projection predictive variable selection approach. The reference model can be used also ad-hoc in combination of common feature selection methods.  In several numerical experiments, we demonstrate superior performance of projection predictive approach and show how use of a reference model translates into better and more stable feature selection independently of the specific selection procedure. 
% These benefits are also illustrated on a real-world example of predicting the amount of body fat for which we compare a reference model based selection method to a purely data driven approach.
\end{abstract}

@@

\begin{table}[tp]
\scriptsize
\centering
\begin{tabular}{l|l|l|l}
 Method & Abbreviation & Type & Quantities of interest \\ 
  \hline
 Regularised Horseshoe & RHS & Shrinkage prior & SSE, SESE, $\kappa$ \\
 Dirichlet-Laplace & DL & Shrinkage prior & SSE, SESE, $\kappa$ \\
 Local false discovery rate & loc.fdr & Complete selection & fdr, sensitivity, stability \\
 Median estimator & EB.med & Complete selection & fdr, sensitivity, stability \\
 Credible intervals & ci.90 & Complete selection & fdr, sensitivity, stability \\
\end{tabular}
\caption{Summary of the shrinkage and selection methods used in the numerical experiments.}
\label{tab:comparison}
\end{table}
